Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

\medskip
Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes. Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}). In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed. The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$. In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh. In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead.

>>>>

Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes. Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}). In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed. The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$. In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh. In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead.
